Tina Paper In Development

### 2024-10-31 docs/writing/paper.tex
Adding more to the intro

\section{Introduction}
The study of tree rings has proven useful across multiple fields, proving to be a reliable subject for reconstructing past climates of regional and local environments, as well as a mechanism to understand tree growth response \citep{fritts_dendroclimatology_1971} \citep{williams_using_2010} \citep{guibal_dendrochronology_2021} \citep{sheppard_dendroclimatology_2010}.
To obtain these data from the tree rings, it is necessary to measure tree rings from a tree cookie or core. The first high precision tool for this purpose was a stage micrometer, involving a trained technician to incrementally shift a tree core under the objective of a microscope - informing a computer when a new ring is encountered \citep{robinson_microcomputer_nodate}.
While this method has very high precision, the data is only as accurate as the experience and knowledge of the technician at the time of recording \citep{levanic_atrics_2007}.
The desire to remove repetition of errors in sampling and sampling bias across to individual technicians led researchers to an alternative - image analysis. 
\par
The first step in measuring tree ring width from images requires the digitization of the sample. There are currently two competing models to digitize a sample. The first model is to use a flatbed scanner or similar tool, to digitize the entire sample at once \citep{guay_new_1992}.
Eventually flatbed scanners have reached a maximum resolution, introducing the second model spawning from ATRICS \citep{levanic_atrics_2007}. A high resolution camera takes multiple images across the surface of the sample, and uses image stitching techniques to combine them into one ultra high resolution image \citep{muhlich_stitching_2022}.
This methodology is often seen in other fields such as mineralogy and cellular biology \citep{ro_image_2021,mohammadi_fast_2024}.

>>>>

\section{Introduction}
The study of tree rings has proven useful across multiple fields, proving to be a reliable subject for reconstructing past climates of regional and local environments, as well as a mechanism to understand tree growth response \citep{fritts_dendroclimatology_1971} \citep{williams_using_2010} \citep{guibal_dendrochronology_2021} \citep{sheppard_dendroclimatology_2010}.
To obtain these data from the tree rings, it is necessary to measure tree rings from a tree cookie or core. The first high precision tool for this purpose was a stage micrometer, involving a trained technician to incrementally shift a tree core under the objective of a microscope - informing a computer when a new ring is encountered \citep{robinson_microcomputer_nodate}.
While this method has very high precision, the data is only as accurate as the experience and knowledge of the technician at the time of recording \citep{levanic_atrics_2007}.
The desire to remove repetition of errors in sampling and sampling bias across to individual technicians led researchers to an alternative - image analysis. 
\par
The first step in measuring tree ring width from images requires the digitization of the sample from one of two major methods.  
The original technique was as a flatbed scanner which can digitize the entire sample at once \citep{guay_new_1992}. 
With a top of the line scanner, like the Epson Perfection V850 Pro, it's possible to scan at maximum resolutions of 4800 dpi. 
The resolution ceiling and a limited scan area of 8.5" x 11.7" make scanners unfit for ultra high resolution analysis or larger samples.

During the time it took for scanners to reach high resolution, the second digitization model was introduced with ATRICS \citep{levanic_atrics_2007}. 
Rather than scanning a whole sample at once, a high resolution camera takes multiple images across the surface of the sample and uses image stitching software techniques to combine them into one ultra high resolution image \citep{muhlich_stitching_2022}.
This methodology is often seen in other fields such as mineralogy and cellular biology \citep{ro_image_2021,mohammadi_fast_2024}. 
This method requires either the camera objective to move relative to the sample, or the sample move underneath a stationary camera. 
For ATRICS and a more modern do-it-yourself alternative, CaptuRING, the sample is moved relative to the camera \citep{garcia-hidalgo_capturing_2022}. 
Gigapixel takes a different approach by moving the camera relative to the sample, allowing for multiple samples to be recorded in sequence.
